Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
improved caption for experiment where we square codebook size
more captions improved

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{
Experiment on squaring the codebook size when the pattern size doubles.
Each line represent $4$ codebook sizes: $2$, $4$, $16$ and $256$.
The pattern size range from $1$ for $1/4$ of a bar to $32$ for $8$ bars.
If everything was random, each of these lines should be flat.
}}
\label{fig:size_pattern}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{Most used codes in the codebook.}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{\small{Locally linear embedding (LLE) visualization of the codebook.}}
\label{fig:lle}
\end{figure}

>>>>

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{
Experiment on squaring the codebook size when the pattern size doubles.
Each line represent $4$ codebook sizes: $2$, $4$, $16$ and $256$.
The pattern size range from $1$ for $1/4$ of a bar to $32$ for $8$ bars.
If everything was random, each of these lines should be flat. The training
size was fixed to $128$K samples.
}}
\label{fig:size_pattern}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set. This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column).
}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{\small{
Locally linear embedding (LLE) visualization of the codebook.
LLE tries to keep near neighbors (here according to euclidean distance)
in the same $2$D neighborhood. Shown patterns were randomly selected
in each neighborhood.
}}
\label{fig:lle}
\end{figure}
